R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
fix #19 text in introduction about why programmatic is important

>>>>

Using programmatic tools for text mining is important for a variety of reasons.
First, using programmatic tools makes it easier for yourself. You can re-run code
to get updated results as data changes, and results can always be re-created.
Second, code can be shared whereas GUI driving workflows can not; colleagues,
reviewers and other researchers can reproduce and check your work. (FIXME: 
re-work this; citations)

### 2019-08-23 manuscript.tex
fix #19 text in introduction about why programmatic is important

Since users can go through a lot of article requests, we cache
successfully downloaded articles, and keep that knowledge consistent
across R sessions; all subsequent requests for the same article just use
the cached version. Additionally, all errors in \texttt{ft\_get()} are
collected in a tidy data.frame in the output of the function to help the
user quickly determine what went wrong.

>>>>

Since users can go through a lot of article requests, we cache
successfully downloaded articles, and keep that knowledge consistent
across R sessions; all subsequent requests for the same article just use
the cached version. Additionally, all errors in \texttt{ft\_get()} are
collected in a data.frame in the output of the function to help the user
quickly determine what went wrong.
